Calendar-based graphics for visualizing people's daily schedules

### 2019-05-15 main.Rmd
More spelling

(ref:facet-cap) Line charts, embedded in the $6 \times 2$ monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.

@@

```{r dow, fig.height = 7, fig.cap = "Boxplots of daily energy usage against day of week for four households. Suggested by the medians, household 3 uses more energy than the others on the week days, due to a large family size. By constrast, household 2 sees considerably larger variability."}
```

@@

```{r hod, fig.height = 6, fig.cap = "Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6, and household 2 around 6, followed by household 3 and 4. The use of air conditioning is noted in household 1 and 2."}
```

@@

# Acknowledgements {-}

>>>>

(ref:facet-cap) Line charts, embedded in the $6 \times 2$ monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasized, and the shapes can be compared across the cells and sensors.

@@

```{r dow, fig.height = 7, fig.cap = "Boxplots of daily energy usage against day of week for four households. Suggested by the medians, household 3 uses more energy than the others on the week days, due to a large family size. By contrast, household 2 sees considerably larger variability."}
```

@@

```{r hod, fig.height = 6, fig.cap = "Scatterplot between half-hourly energy usage and time of day with the averages overlaid, contrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6, and household 2 around 6, followed by household 3 and 4. The use of air conditioning is noted in household 1 and 2."}
```

@@

# Acknowledgments {-}
